### 2019-10-16 defesa/tex/chapter/e3p.tex
wip

In this section we run some experiments to verify how big the interpolation degree must be for a good precision to be achieved. Let $f_n$ be the $n$-degree Chebyshev interpolation of $\xi$, we measure the error by using the infinite norm:

\begin{equation}
r_n = \max_{0 \le \theta \le \pi} |f_n(\theta) - \xi(\theta)|
\end{equation}

>>>>

In this section we run some experiments to verify how big the interpolation degree must be for a good precision to be achieved. 
Let $f_n$ be the $n$-degree Chebyshev interpolation of $\xi$, we define the interpolation error $r_n$ as:

\begin{equation}
r_n = \max_{0 \le \theta \le \pi} |f_n(\theta) - \xi(\theta)|.
\end{equation}

Then, we want to determine the smallest $n$, such that $r_n \le \epsilon$, for a predefined $\epsilon$. Unfortunately, calculating $r_n$ involves taking samples from both functions on the whole interval, which is not viable computationally. In \citeonline[p.~50]{boyd:2001} a rule-thumb for estimating the interpolation error is given. It is worth mentioning that this rule

It uses a theorem that states that $r_n$ is limited by the sum of the coefficients of the Chebyshev series that were removed by the truncation. The rule-of-thumb for estimating $r_n$ is given by:

\begin{equation}
r_n \approx |a_n|.
\end{equation}

Note that

Obtaining an expression for it is not trivial, and sampling the whole interval is not viable computationally.

Therefore, an estimation of $r_n$ is used to measure how good is the approximation.
